Our results suggest that bubble dynamics are be strongly influenced by timing effects. Traditional network measures based on introduciers position in the discussion graph provide some aditional  information beyond this.

As future work we are looking at coarse (positive/negative, detailed/cursory) semantic analysis of the discussion, and evidence of prior cooperation between pairs of participants in other altcoin markets, in order to attempt a more accurate characterization of core participants and their actions.
The features of the node as well as the construction of the social graph are informed by a the pre-existing literature which does not allow for much complexity on the edges of the graphs beyond weight and direction.
A promising avenue for future work is to explore richer models for edges. Allowing them to exist in latent spaces, where the influence or attnetion that is payed by responding to a user is mediated by the wording of the response. 

While removing fears of reverse causality, the cross-sectional design with time separation does not allow us to take advantage of intra-coin price variation, which can potentially be very informative.
In particular models that looked at disagregated prices accross the different exchanges, could use measures of price dispersion and potential arbitrage oportunities to gain a richer understanding of the outcome space.

Beyond using data from forums, code repositories could also be exploited in future work as a rich source of variation beyond the binary feature of whether a coin is a trivial fork or not, as well as offering a expanded view of the social interactions network.


While the period of active speculation in these alternative cryptocurrencies seems to be largely over, further speculative markets seem likely to emerge in the future. Comparative analysis over mutliple social structures of speculative bubbles that have disagregated infromation could allow for much more refined tests of theories. 
All data and code in this paper is public (including tools for scrapping it and disargegated raw price and forum data), and substantial effort has been made to docuement it, so it can be used in such future investigations. 
